Viscous Transport in Eroding Porous Media

### 2019-08-25 docs/transport/erosion_transport.tex
started to go through results section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Flow in many natural occurring geometries involves flows that vary over
many orders of magnitude.  \todo[]{The grammar in the first sentence is awkward: Flow in ... involves flows?}
For example, the length scales of a porous
media can vary from $10^{-6}m$ to
$10^{-1}m$~\cite{mil-chr-imh-mcb-ped1998}.  Porous media flow plays an
important role in several environmental and industrial applications.
Therefore, understanding the dynamics of pore-scale flow is central to
upscale the governing fluid equations, characterize
dispersion~\cite{saf1959}, and quantify mixing. However, because of the
large disparity of length and velocity scales, constitutive laws that
link the microscopic scale to macroscopic scale must be
developed~\cite{mil-chr-imh-mcb-ped1998}.  Therefore, to find closure
formulas, accurate simulations at microscopic scales must be performed
and analyzed.  A few examples of closure formulas and coarse-grained
variables include
pressure-saturation-permeability~\cite{mil-chr-imh-mcb-ped1998},
permeability-porosity~\cite{dar-mcc1998, car1937, won-kop-tom1984},
first passage time distribution~\cite{ber-sch-sil2000,
hym-den-hag-kan2019, cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
matyka2008tortuosity, dud-koz-mat2011, kop-kat-tim1996}, concentration
distributions~\cite{ica-den2019, bel-sal-rin1992}, flow
distributions~\cite{ali-par-wei-bre2017}, geometry
connectivity~\cite{knu-car2005, wes-blo-gra2001}, pore
distributions~\cite{ali-par-wei-bre2017}, and anomalous
dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
sie-ili-pri-riv-gua2019}.

@@

In a porous geometry, the length of a particle path is larger than the
distance travelled if the grains were absent.  To quantify the amount of
winding a particle takes, we use the tortuosity that is defined as the
ratio of the particle paths length to the distance between the inlet and
outlet.  In fractured media, the local tortuosity can be over
2.5~\cite{hym-den-hag-kan2019}, and in porous media, depending on the
porosity, the local tortuosity can be greater than
1.5~\cite{kop-kat-tim1996, matyka2008tortuosity}, or greater than
2~\cite{dud-koz-mat2011}.  The tortuosity of the geometry is defined by
averaging over the entire inlet.  Therefore, the geometry's tortuosity
can be used to characterize average particle
motions~\cite{hak-com-den2019}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Anomalous Disperision}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The dynamics of fluid in porous media is often characterized in terms of
anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
anomalous dispersion rate depends on the porosity and
permeability~\cite{koc-bra1988}, but the distribution of the bodies also
affects the anomalous dispersion rates.  Since erosion causes certain
structure in porous media, calculating the anomalous dispersion rates in
these geometries is important.

We calculate the anomalous dispersion rates by analyzing the tracer
trajectories governed by equation~\eqref{eqn:tracers} for geometries
that are formed by erosion.  Given a set of trajectories, we define
$\lambda_j(t)$ to be the arclength of the trajectory
\begin{align}
  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
    \quad j=1,\ldots,N_p.
\end{align}
Then, the first and second ensemble moments are
\begin{align}
  \langle \lambda \rangle (t) = 
    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
    \sigma_\lambda^2(t) = \frac{1}{N_p} 
    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
\end{align}
Since we compute second-order statistics, we use 1000 tracers so that
the statistics have converged~\cite{bel-sal-rin1992}.  Then, particle
dispersion is characterized as $\sigma_\lambda$.  At early times, the
particles have not explored much of the geometry, and we expect a
ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
pass the grains, their trajectories are altered, and we expect that
$\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$, indicating
that the flow is super-dispersive.

@@

There have been efforts to relate the tortuosity to the
porosity~\cite{matyka2008tortuosity}.  For example, Matyka et
al.~\cite{matyka2008tortuosity} propose the models
\begin{subequations}
  \label{eqn:tortuosityModels}
  \begin{align}
    \widehat{T}(\phi) &= \phi^{-p}, \\
    \widehat{T}(\phi) &= 1-p \log \phi, \\
    \widehat{T}(\phi) &= 1+p (1-\phi), \\
    \widehat{T}(\phi) &= (1+p (1-\phi))^2, 
  \end{align}
\end{subequations}
where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
compare these four models with the tortuosity of eroding geometries.

@@

Per grid point, applying the Barycentric quadrature rules dominates the
computational cost. Therefore, it is imperative that we only apply the
Barycentric quadrature when the trapezoid rule is inaccurate.  As a rule
of thumb, the trapezoid rule due to $\gamma_k$ achieves machine epsilon
accuracy if~\cite{bar2014}
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we check if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a parameter that needs to be chosen.  In
this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} \right).
\end{align}
To determine if points on $\gamma_i$ are too close to the outer wall, we
recall that the outer wall is bounded in $[-3,3] \times [-1,1]$, and
that the bodies are all contained in $[-1,1] \times [-1,1]$.  Therefore,
a target point can only be too close to the lines $y = \pm 1$, so we
first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_i \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out},
\end{align}
\todo[inline]{Bryan is here}
where $x_i$ is the x coordinate of $\cc_i$. If body $\gamma_i$ satisfies
this condition, for each point $\xx=(x,y) \in \gamma_i$, we apply the
Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}
Finally, to determine if a target point $\xx$ that is in the fluid bulk
rather than on another eroding body requires the Barycentric quadrature
rule, we only check conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we fix a eroded geometry and we compute an accurate solution by using
the Barycentric quadrature rule for all discretization points.  Then,
for multiple values of $\alpha_\iin$ and $\alpha_\out$, we compute the
velocity field with the trapezoid rule for all points that do not
satisfy conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that $\alpha_\iin = 4$ and $\alpha_\out = 4$ give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.  We use these values for all
of our numerical simulations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Integration}
\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We reuse the time stepping method outlined in our previous
work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$ coordinates,
the {\thL} variables are tracked. In addition, a tangential velocity
field is added to each body so that the discretization points remain
equispaced for all time.  A second-order Implicit-Explicit method is
used. In particular, the diffusive term corresponding to the curvature
penalization term is discretized implicitly, and all other terms, which
are non-stiff, are treated explicitly.  By using this time stepping
method in conjunction with the curvature penalization and Gaussian
filter, we stably evolve the eroding bodies.   An in depth description
of the time stepping method for erosion is in Section 3.3 of our
previous work~\cite{qua-moo2018}.

In Section~\ref{sec:transport}, we require trajectories of passive
tracers passing through an eroded geometry.  Given such a geometry
$\Omega$, a tracer $\ss(t)$ initialized at $\ss_0$ is governed by 
\begin{align}
  \label{eqn:trajectories}
  \frac{d\ss}{dt} = \uu(\ss), \quad \ss(0) = \ss_0.
\end{align}
To compute such a trajectory, we apply the standard explicit
fourth-order Runge-Kutta method.  To evaluate $\uu(\ss)$, depending on
the proximity of $\ss(t)$ to $\bd\Omega$, we either use the trapezoid
rule or the Barycentric quadrature rule as described in
Section~\ref{sec:fmm}.

\todo[inline]{Dump of text}
The first method to numerically compute the tortuosity uses $N_p$
trajectories that are initialized at $(-1,y_i)$, $i=1,\ldots,N_p$, and
stopped when their $x$ coordinate is 1.  We choose $y_i$ so that the
trajectories are initially uniformly spaced in $(-1,1)$.  Having
computed these trajectories, the tortuosity is approximated as
\begin{align}
  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
    u_x(y_i) \lambda(y_i) \Delta y}
  {\displaystyle\sum_{i=1}^{N_p} u_x(y_i) \Delta y}, 
\end{align}
where $\Delta y = 2/(N_p + 1)$ and $y_i = -1 + i \Delta y$,
$i=1,\ldots,N_p$.

Having developed numerically accurate methods to compute the velocity
$\uu$ at points close to the bodies, we are able to compute the
trajectories of particles passing through an eroded body.  Since the
trajectories are computed with high-order methods in both space and
time,  we are able to simulate dynamics very close to the eroding bodies
(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.

\todo[inline]{Dump of text}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section, we apply our new quadrature method to simulate erosion
of several different configurations of eroding bodies.  The fluid domain
is $\Omega$ whose outer solid walls is a rectangle $[-3,3] \times
[-1,1]$ with rounded off corners.  We initialize the bodies randomly in
$[-1,1] \times [-1,1]$ using a randomized method that chooses a random
center and radii, and then accepts the new body if it is sufficiently
separated from all other bodies.  Since the error of our quadrature
method is bounded independent of the geometry, we consider bodies that
are separated by less than 10\% of an arclength spacing.  For all
simulations, we discretize $\Gamma = \bd \Omega$ with $N_\out=1024$
points.  For all but the first example, the Dirichlet boundary condition
on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
rate is adjusted to maintain the physical constant pressure drop
boundary condition.  To maintain this pressure drop, we compute the
pressure at near the inlet and outlet at each time step as described in
our previous work~\cite{qua-moo2018}.

The initial shape of the eroding body $\gamma_i$ is a circle centered at
$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
$\gamma_i$ is discretized with $N_\iin$ points.  A no-slip boundary
condition is imposed on $\gamma_i$.  The initial configuration is
constructed with an annealing algorithm and has the desired initial
porosity, and a user-specified minimum distance between any two eroding
bodies and the eroding body and solid wall.  To round off inevitable
corners on the eroding bodies, for all simulations we apply smoothing
the smoothing parameters $\eps=15/256$ and $\sigma=10/256$, as described
in~\cite{qua-moo2018}.

The common characteristic of each of the experiments is near-contact
between the eroding bodies and outer walls. Once we have simulated
erosion, we compute velocities, streamlines, trajectories, and vorticity
so that the flow can be visualized and analyzed.  The experiments we
perform are:
\begin{itemize}
  \item{\bf Single Body Close to a Wall}: We consider a single eroding
  body close to the outer wall at $y=-1$.  Using a shear flow that
  vanishes on $y=-1$, we compare the eroding body's shape to a similar
  experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.

@@

  \item{\bf 50 Bodies at a Low Porosity}: We consider 50 eroding bodies
  with a low initial porosity.  In addition to the tortuosity and
  anomalous dispersion rates, we compute distributions of the pore
  throat sizes and examine their response to erosion.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather than a pressure drop boundary
condition, we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  In their experiment, Mitchell and Spagnolie place
the center of the eroding body $1.5$ times the body's radius above the
solid wall.  By using the Barycentric quadrature rule described in
Section~\ref{sec:bary} rather than the trapezoid rule, the eroding body
can be placed much closer to the solid wall without requiring an
unreasonable number of discretization points.  We consider an eroding
body that is initially a circle of radius $r=0.4$.  We discretize the
eroding body with $N_\iin=256$ discretization points, and its center is
chosen so that the distance between the body and the solid wall is
$h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all three
simulations, we use the time step size $\Delta t=10^{-4}$.

In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
equispaced time steps.  For the three initial configurations, the shear
stress is positive for all time, but varies over several orders of
magnitude.  Therefore, we color the eroding body's boundary with the
logarithm of the shear stress.  Since the shear stress is always
positive, the erosion rate is a smooth function and does not lead to the
development of corners.  However, the shear stress varies over several
orders of magnitude, and this leads to interesting shapes.  For
instance, in the top hemisphere, there is a sudden increase in the shear
stress, and this leads to a region of high curvature.  This behavior is
also present in three dimensions~\cite{mit-spa2017} (Figure 7(c)).  The
biggest difference between the two- and three-dimensional results is the
presence of a recirculation zone.  In three dimensions, there is no
recirculation between the solid wall and the spherical
body~\cite{cha-feu2003}.  In contrast, the two-dimensional flow Stokes
flow can have recirculation zones~\cite{chw-wu1975, hig1985}. To
visualize the flow, we plot the vorticity of the final time step from
Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  The region
where the vorticity is smallest corresponds to the recirculation region.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Flow in many natural occurring geometries involves flows that vary over
many orders of magnitude.  \todo[]{The grammar in the first sentence is awkward: Flow in ... involves flows?}
For example, the length scales of a porous
media can vary from $10^{-6}m$ to
$10^{-1}m$~\cite{mil-chr-imh-mcb-ped1998}.  Porous media flow plays an
important role in several environmental and industrial applications.
Therefore, understanding the dynamics of pore-scale flow is central to
upscale the governing fluid equations, characterize
dispersion~\cite{saf1959}, and quantify mixing. However, because of the
large disparity of length and velocity scales, constitutive laws that
link the microscopic scale to macroscopic scale must be
developed~\cite{mil-chr-imh-mcb-ped1998}.  Therefore, to find closure
formulas, accurate simulations at microscopic scales must be performed
and analyzed.  A few examples of closure formulas and coarse-grained
variables include
pressure-saturation-permeability~\cite{mil-chr-imh-mcb-ped1998},
permeability-porosity~\cite{dar-mcc1998, car1937, won-kop-tom1984},
first passage time distribution~\cite{ber-sch-sil2000,
hym-den-hag-kan2019, cve-che-wen1996}, tortuosity~\cite{hak-com-den2019,
mat-kha-koz2008, dud-koz-mat2011, kop-kat-tim1996}, concentration
distributions~\cite{ica-den2019, bel-sal-rin1992}, flow
distributions~\cite{ali-par-wei-bre2017}, geometry
connectivity~\cite{knu-car2005, wes-blo-gra2001}, pore
distributions~\cite{ali-par-wei-bre2017}, and anomalous
dispersion~\cite{dea-qua-bir-jua2018, den-cor-sch-ber2004,
sie-ili-pri-riv-gua2019}.

@@

In a porous geometry, the length of a particle path is larger than the
distance travelled if the grains were absent.  To quantify the amount of
winding a particle takes, we use the tortuosity that is defined as the
ratio of the particle paths length to the distance between the inlet and
outlet.  In fractured media, the local tortuosity can be over
2.5~\cite{hym-den-hag-kan2019}, and in porous media, depending on the
porosity, the local tortuosity can be greater than
1.5~\cite{kop-kat-tim1996, mat-kha-koz2008}, or greater than
2~\cite{dud-koz-mat2011}.  The tortuosity of the geometry is defined by
averaging over the entire inlet.  Therefore, the geometry's tortuosity
can be used to characterize average particle
motions~\cite{hak-com-den2019}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Anomalous Disperision}
\label{sec:dispersion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The dynamics of fluid in porous media is often characterized in terms of
anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.  The
anomalous dispersion rate depends on the porosity and
permeability~\cite{koc-bra1988}, but the distribution of the bodies also
affects the anomalous dispersion rates.  Since erosion causes certain
structure in porous media, calculating the anomalous dispersion rates in
these geometries is important.

We calculate the anomalous dispersion rates by analyzing the tracer
trajectories governed by equation~\eqref{eqn:tracers} for geometries
that are formed by erosion.  Given a set of trajectories, we define
$\lambda_j(t)$ to be the arclength of the trajectory
\begin{align}
  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
    \quad j=1,\ldots,N_p.
\end{align}
Then, the first and second ensemble moments are
\begin{align}
  \label{eqn:moments}
  \langle \lambda \rangle (t) = 
    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
    \sigma_\lambda^2(t) = \frac{1}{N_p} 
    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2.
\end{align}
Since we compute second-order statistics, we use 1000 tracers so that
the statistics have converged~\cite{bel-sal-rin1992}.  Then, particle
dispersion is characterized as $\sigma_\lambda$.  At early times, the
particles have not explored much of the geometry, and we expect a
ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
pass the grains, their trajectories are altered, and we expect that
$\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$, indicating
that the flow is super-dispersive.

@@

There have been efforts to relate the tortuosity to the porosity.  For
example, Matyka et al.~\cite{mat-kha-koz2008} propose the models
\begin{subequations}
  \label{eqn:tortuosityModels}
  \begin{align}
    \widehat{T}(\phi) &= \phi^{-p}, \\
    \widehat{T}(\phi) &= 1-p \log \phi, \\
    \widehat{T}(\phi) &= 1+p (1-\phi), \\
    \widehat{T}(\phi) &= (1+p (1-\phi))^2, 
  \end{align}
\end{subequations}
where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
compare these four models with the tortuosity of eroding geometries.

@@

Per grid point, applying the Barycentric quadrature rules dominates the
computational cost. Therefore, it is imperative that we only apply the
Barycentric quadrature when the trapezoid rule is inaccurate.  As a rule
of thumb, the trapezoid rule due to $\gamma_k$ achieves machine epsilon
accuracy if~\cite{bar2014}
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we check if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a parameter that needs to be chosen.  In
this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} \right).
\end{align}
To determine if points on $\gamma_i$ are too close to the outer wall, we
recall that the geometry is contained in a rounded-off version of
$[-3,3] \times [-1,1]$, and that the bodies are all contained in $[-1,1]
\times [-1,1]$, so a target point can only be too close to the lines $y
= \pm 1$. Therefore, we first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_i \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out},
\end{align}
where $x_i$ is the x coordinate of $\cc_i$. If body $\gamma_i$ satisfies
this condition, for each point $\xx=(x,y) \in \gamma_i$, we apply the
Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}
Finally, to determine if a target point $\xx$ in the fluid bulk requires
the Barycentric quadrature rule, we only check
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we fixed an eroded geometry and computed an accurate solution by using
the Barycentric quadrature rule for all discretization points.  Then,
for multiple values of $\alpha_\iin$ and $\alpha_\out$, we computed the
velocity field with the trapezoid rule for all points that do not
satisfy conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that $\alpha_\iin = 4$ and $\alpha_\out = 4$ give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.  We use these values for all
of our numerical simulations.
\todo[inline]{S-H: What kind of accuracy did this give?  This is less
than the value used by Barnett in his single author quadrature paper.
He said that 5 arclength spacings is the right amount to guarantee
machine precision.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Integration}
\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We reuse the time stepping method outlined in our previous
work~\cite{qua-moo2018} which we briefly summarize here.  Rather than
tracking the $(x,y)$ coordinates, the {\thL} variables are tracked. In
addition, a tangential velocity field is added to each body so that the
discretization points remain equispaced in arclength for all time.  A
second-order Implicit-Explicit Runge-Kutta method is used. In
particular, the diffusive term corresponding to the curvature
penalization term is discretized implicitly, and all other terms, which
are non-stiff, are treated explicitly.  By using this time stepping
method in conjunction, we stably evolve the eroding bodies.   An in
depth description of the time stepping method for erosion is in Section
3.3 of our previous work~\cite{qua-moo2018}.

To compute the tortuosity and the anomalous dispersion rates
(Section~\ref{sec:transport}), we require trajectories of passive
tracers, governed by equation~\eqref{eqn:tracers}.  To reliably
characterize the transport, it is crucial that the trajectories are
computed accurately.  If a low-order time stepping method is used, or if
$\uu(\ss(t))$ is inaccurate, then a trajectory $\ss(t)$ can unphysically
enter a grain, rendering the trajectory meaningless to quantify
transport.  However, if we simply ignored trajectories that pass close
to grains, this would considerably skew the characterization of the
transport. Therefore, we use high-order quadrature and time stepping
methods.  In particular, depending on the proximity of $\ss(t)$ to
$\bd\Omega$ (Section~\ref{sec:fmm}, we apply the trapezoid rule or the
Barycentric quadrature rule.  For time stepping, we use a fourth-order
explicit Runge-Kutta method.  Since the trajectories are computed with
high-order methods in both space and time,  we are able to simulate
dynamics very close to the eroding bodies (see
Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}).

Once a collection of trajectories are formed, they are used to quantify
the dispersion and the tortuosity.  The dispersion simply computes the
second-moment of the trajectories as described in
equation~\eqref{eqn:moments}.  However, as described in
Section~\ref{sec:dispersion}, a reinsertion method is used to compute
trajectories that are sufficiently long to observe an asymptotic
anomalous dispersion rate.  To compute the tortuosity using the
trajectories, we consider trajectories crossing between the two
cross-sections $x=-1$ and $x=1$.  Then, we discretize
equation~\eqref{eqn:tortuosity1} as
\begin{align}
  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N_p} 
    u_x(y_i) \lambda(y_i) \Delta y}
  {\displaystyle\sum_{i=1}^{N_p} u_x(y_i) \Delta y}, 
\end{align}
where $\Delta y = 2/(N_p + 1)$ and $y_i = -1 + i \Delta y$,
$i=1,\ldots,N_p$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section, we apply our new quadrature method to (1) simulate
erosion of several different configurations of eroding bodies, and (2)
characterize transport inside eroded geometries.  Each eroding body is
initially a circle with center $\cc_i$ and radius $r_i$.  The center and
radius are chosen at random, and the body is accepted as long as it is
contained in $[-1,1] \times [-1,1]$ and is sufficiently separated from
all other bodies.  Since the error of our quadrature method is bounded
independent of the geometry, we consider bodies that are separated by
less than 10\% of an arclength spacing.  The randomized method is
repeated until the initial geometry reaches a desired initial porosity.

Once the geometry is initialized, each body has length $L_i = 2\pi r_i$,
and they are each discretized with $N_\iin$ points.  A no-slip boundary
condition is imposed on each eroding body $\gamma_i$.  For all
simulations, we discretize the outer wall $\Gamma$ with $N_\out=1024$
points.  For all but the first example, the Dirichlet boundary condition
on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
rate is adjusted to maintain the physical constant pressure drop
boundary condition.  To maintain this pressure drop, we compute the
pressure at near the inlet and outlet at each time step as described in
our previous work~\cite{qua-moo2018}.

In each of the examples, we include plots of the vorticity in the fluid
bulk.  Since the vorticity and the shear stress agree on surface of the
eroding bodies, the vorticity is a useful method to visualize the
erosion rate.  In particular, the rate of erosion is largest in regions
where the magnitude of the vorticity is largest.

Because of the definition of the erosion rate, there is a loss of
regularity, and this inevitably leads to corners developing on the
eroding bodies.  Therefore, as described in
Section~\ref{sec:formulation} and our previous work~\cite{qua-moo2018},
we introduce a curvature penalization term and a Gaussian smoothing
step.  For all examples, we use the smoothing parameters $\eps=15/256$
and $\sigma=10/256$.

The common characteristic of each of the experiments is near-contact
between the eroding bodies, outer walls, and passive tracers. We use our
numerical methods to describe and visualize the following examples:
\begin{itemize}
  \item{\bf Single Body Close to a Wall}: We consider a single eroding
  body close to the outer wall at $y=-1$.  Using a shear flow that
  vanishes on $y=-1$, we compare the eroding body's shape to a similar
  experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather than a pressure drop boundary
condition, we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  In their experiment, Mitchell and Spagnolie place
the center of the eroding body $1.5$ times the body's radius above the
solid wall.  By using the Barycentric quadrature rule described in
Section~\ref{sec:bary} rather than the trapezoid rule, the eroding body
can be placed much closer to the solid wall without requiring an
unreasonable number of discretization points.  We consider an eroding
body that is initially a circle of radius $r=0.4$.  We discretize the
eroding body with $N_\iin=256$ discretization points, and its center is
chosen so that the distance between the body and the solid wall is
$h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  If we were to use
the trapezoid rule and require an error that is comparable to the
Barycentric quadrature rule, the body with an initial distance of $h/10$
from the solid wall would require $6,400$ discretization points, and the
outer wall would require $50,000$ discretization points.  For all three
simulations, we use the time step size $\Delta t=10^{-4}$.

In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
equispaced time steps.  For the three initial configurations, the shear
stress is positive for all time, but varies over several orders of
magnitude.  Therefore, we color the eroding body's boundary with the
logarithm of the shear stress.  Since the shear stress is always
positive, the erosion rate is smooth and corners do not develop.
However, the shear stress varies over several orders of magnitude, and
this leads to interesting shapes.  For instance, in the top half of the
body, there is a sudden increase in the shear stress, and this leads to
a region of high curvature.  This behavior is also present in three
dimensions~\cite{mit-spa2017} (Figure 7(c)).  The biggest difference
between the two- and three-dimensional results is the presence of a
recirculation zone.  In three dimensions, there is no recirculation
between the solid wall and the spherical body~\cite{cha-feu2003}.  In
contrast, the two-dimensional flow Stokes flow can have recirculation
zones~\cite{chw-wu1975, hig1985}. To visualize the flow, we plot the
vorticity of the final time step from Figure~\ref{fig:NearWall} in
Figure~\ref{fig:NearWall_vort}.  The recirculation is present in the
region where the vorticity is smallest.
